\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2012-05-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
new developers

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Min Chen,
Hom Nath Gharti,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
Matthias Meschede,
David Mich\'ea,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Hejun Zhu.\\
%\toall{add full list of developers here and update the AUTHORS file accordingly}

>>>>

Since then it has been developed and maintained by a development team: in alphabetical order,
Piero Basini,
C\'eline Blitz,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Hom Nath Gharti,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Dennis McRitchie,
Matthias Meschede,
David Mich\'ea,
Tarje Nissen-Meyer,
Daniel Peter,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Zhinan Xie,
Hejun Zhu.\\
%\toall{add full list of developers here and update the AUTHORS file accordingly}
